### 2018-01-29 includes/prior.tex
Fixing typos and descriptions.
one pass all the way to the end. Conclusion and related work need work.

    There are likewise several fuzzers and problem generators currently available, but none of them can generate or transform string and regex problems. For example the FuzzSMT\cite{fuzzsmt} tool generates \smt{} problems with bit vectors and arrays, but does not support strings or regexes. The SMTpp\cite{smtpp} tool preprocesses and simplifies problems, but does not generate new ones or fuzz existing ones.

>>>>

    There are likewise several fuzzers and problem generators currently available.
    However, none of these fuzzers can generate and transform string and regex problems. 
    \todo{I know we talked about this one before, but I'm confused by it again.}
    For example the FuzzSMT\cite{fuzzsmt} tool generates \smt{} problems with bit vectors and arrays, 
    but does not support strings or regexes. 
    The SMTpp\cite{smtpp} tool pre-processes and simplifies problems, but does not generate new ones or fuzz existing ones.
